### 2018-09-03 Sections/quality_of_service.tex

\begin{figure}[!htbp]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{} & \qw & \targ & \meter \\
		\lstick{} & \qw & \ctrl{-1} & \qw
		} \nonumber
	\end{align}
	\captionspace \caption{Construction of a parity measurement circuit using a single CNOT gate and a single-qubit measurement. The measurement outcome indicates whether the two input qubits were the same (\mbox{$\ket{0}\ket{0}$}, \mbox{$\ket{1}\ket{1}$}) or different (\mbox{$\ket{0}\ket{1}$}, \mbox{$\ket{1}\ket{0}$}). See Sec.~\ref{sec:bell_proj} for a simple linear optics construction for this operation.}\label{fig:parity_meas}\index{Bell measurements}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.39\textwidth]{entanglement_purification}
\captionspace \caption{Protocol for entanglement purification of two noisy Bell pairs (blue) into a single less noisy Bell pair. Not shown are trivial single-qubit local corrections that may need to be made, depending upon measurement outcomes.} \label{fig:ent_purif_circ}\index{Entanglement purification protocol}
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function ThreeQubitCode($\ket\psi$):
\begin{enumerate}
\item Using two CNOT gates, redundantly encode the logical single-qubit state,
\begin{align}
\ket\psi=\alpha\ket{0}+\beta\ket{1},
\end{align}
into the 3-qubit state,
\begin{align}
\ket\psi_R &= \hat{\mathrm{CNOT}}_{1,2}\hat{\mathrm{CNOT}}_{1,3}\ket\psi\ket{00} \nonumber \\
&= \alpha\ket{000}+\beta\ket{111}.
\end{align}
\item Independently apply bit-flip channels $\mathcal{E}_X$ to each of the three encoded qubits.
\item If exactly one bit-flip operation was applied in total, the three possible erroneous encoded states are,
\begin{align}
\ket\psi_1 &= \hat{X}_1 \ket\psi_R = \alpha\ket{001}+\beta\ket{110}, \nonumber \\
\ket\psi_2 &= \hat{X}_2 \ket\psi_R = \alpha\ket{010}+\beta\ket{101}, \nonumber \\
\ket\psi_3 &= \hat{X}_3 \ket\psi_R = \alpha\ket{100}+\beta\ket{011}.
\end{align}
\item Determine the parity of each of the three pairs of encoded qubits.
\item Assuming at most a single bit-flip operation has occurred on the encoded state, the three parity outcomes uniquely determine which encoded qubit the bit-flip was applied to.
\item Apply classically-controlled bit-flip recovery operations, $\mathcal{R}$, to correct the encoded state, recovering $\ket\psi_R$.
\item Apply the inverse of the encoding operation to recover $\ket\psi$.
\item $\Box$
\end{enumerate}}
\begin{align}
\Qcircuit @C=1.3em @R=.6em {
  & \lstick{\ket{\psi}} & \ctrl{2} & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{3}  & \qw       & \ctrl{4} & \qw & \multigate{2}{\ \mathcal{R}\ } & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{2}  & \ctrl{2}  & \qw      & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \qw       & \ctrl{2}  & \ctrl{3} & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  &          &          &          & & \lstick{\ket{0}} & \targ \qw & \qw       & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \targ \qw & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \qw       & \targ    & \meter & \control \cw \cwx
} \nonumber
\end{align}
\end{mdframed}
\captionspace \caption{3-qubit code for protecting against at most a single logical bit-flip error. The doubly-controlled CNOT gates represent parity measurements, \mbox{$n_3=n_1\oplus n_2$}, where $n_i$ represents the value of the $i$th qubit. In a Hadamard-rotated basis, the same circuit may be employed to protect against a single phase-flip error. And by concatenating the two we obtain a 9-qubit code protecting against a single depolarising error (i.e joint bit-flip/phase-flip), which is a universal single-qubit error model.} \label{alg:three_QEC}
\end{table}

@@

\if 2\pubmode
	\begin{figure}[!htbp]
		\includegraphics[width=0.475\textwidth]{torus}\\
		\includegraphics[width=0.475\textwidth]{toric_code}
		\captionspace \caption{Graph representation of the toric QEC code, and its associated stabilisers. The graph resides on a torus (top), while the physical qubits reside on the embedded lattice (bottom). The star and plaquette stabilisers across all vertices, jointly specify the state of the graph up to two missing degrees of freedom, which encode a single logical qubit. Thus, a logical qubit is encoded jointly across the entire graph, not at any specific vertex. Logical operations are performed via operations following topological paths through the lattice (not shown). The graph may be distributed across multiple hosts for distributed quantum computation.} \label{fig:toric_code}
	\end{figure}
\else
	\begin{figure*}[!htbp]
		\includegraphics[width=0.475\textwidth]{torus}
		\includegraphics[width=0.475\textwidth]{toric_code}
		\captionspace \caption{Graph representation of the toric QEC code, and its associated stabilisers. The graph resides on a torus (left), while the physical qubits reside on the embedded lattice (right). The star and plaquette stabilisers across all vertices, jointly specify the state of the graph up to two missing degrees of freedom, which encode a single logical qubit. Thus, a logical qubit is encoded jointly across the entire graph, not at any specific vertex. Logical operations are performed via operations following topological paths through the lattice (not shown). The graph may be distributed across multiple hosts for distributed quantum computation.} \label{fig:toric_code}
	\end{figure*}
\fi

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.3\textwidth]{toric_code_correction}
	\captionspace \caption{QEC of a single bit-flip (top) and phase-flip (bottom) error via measuring two overlapping stabilisers. If there is at most one bit- or phase-flip error, as per this graphic, then upon measuring all the star and plaquette stabilisers, only those whose qubits are affected by the error channel will yield the $-1$ measurement outcome, the others all yielding $+1$. Such an error will affect exactly two stabilisers, whose qubit in common must have been the one affected by the respective error, which can subsequently be corrected since the type of the error and its location are known. Thus, in this example, all of the $\hat{S}_+^{(1)}$, $\hat{S}_+^{(2)}$, $\hat{S}_\square^{(1)}$ and $\hat{S}_\square^{(2)}$ stabilisers will yield $-1$ outcomes for the shown $\hat{X}$ and $\hat{Z}$ errors, whereas any of the remaining (not shown) $\hat{S}_k^{(j)}$ will yield $+1$ outcomes, which uniquely specifies where those errors took place.}\label{fig:toric_corr}	
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{torus_paulis}
	\captionspace \caption{Implementation of logical Pauli-$\hat{X}$ (\comment{which colour?}) and -$\hat{Z}$ (\comment{which colour?}) operations on a toric code qubit via the application of a chain of local Paulis. The chains must circumnavigate the torus around either axis. Any path topologically equivalent to such a circumnavigation of the torus is sufficient, enabling paths to bypass defects in the lattice.} \label{fig:toric_code_paulis}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{unitary_error_averaging}
\captionspace \caption{Protocol for error correction via unitary error averaging. Here our computation resides across \mbox{$N=2$} modes, and there are \mbox{$M=2$} redundant copies of the manufactured unitary, which straightforwardly generalises to arbitrary $M$ and $N$. A fanout operation splits the wave amplitudes from the set of $N$ input modes uniformly across $M$ sets of $N$ modes. Each set of $N$ evolves through an independent copy of the manufactured imperfect unitary, $\tilde{U}_i$. A reverse fanout operation recollects the bundles of modes. Upon post-selecting upon detecting all photons within the first $N$ modes, and none in the other ancillary modes, the state is projected into the subspace as if it had been acted upon by the arithmetic average of the imperfect unitaries. If photons are detected in the error modes, our logical state has effectively suffered photon loss and has been corrupted.} \label{fig:error_av_circuit}	
\end{figure}

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{bloch_sphere_dyn_dec_long}
	\captionspace \caption{Bloch sphere representation of a sequence to dynamically decouple an unknown $\hat{Z}$ rotation from a qubit. (a) Blue dot represents the initial state. (b) The state undergoes an unknown $\hat{Z}(\theta)$ rotation. (c) A bit-flip ($\hat{X}$) flips the Bloch sphere upside down. (d) Waiting for the same time as before such that the same unknown $\hat{Z}$-rotation takes place, the state ends up in its initial state, independent of the $\hat{Z}$-rotation angle $\theta$, but assuming it was the same on both occasions in (b) and (d).} \label{fig:bloch_sphere_dyn_dec}	
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=\textwidth]{bloch_sphere_dyn_dec}
	\captionspace \caption{Bloch sphere representation of a sequence to dynamically decouple an unknown $\hat{Z}$ rotation from a qubit. (a) Blue dot represents the initial state. (b) The state undergoes an unknown $\hat{Z}(\theta)$ rotation. (c) A bit-flip ($\hat{X}$) flips the Bloch sphere upside down. (d) Waiting for the same time as before such that the same unknown $\hat{Z}$-rotation takes place, the state ends up in its initial state, independent of the $\hat{Z}$-rotation angle $\theta$, but assuming it was the same on both occasions in (b) and (d).} \label{fig:bloch_sphere_dyn_dec}	
	\end{figure*}
\fi

>>>>

\begin{figure}[!htbp]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{} & \qw & \targ & \meter \\
		\lstick{} & \qw & \ctrl{-1} & \qw
		} \nonumber
	\end{align}
	\captionspacefig \caption{Construction of a parity measurement circuit using a single CNOT gate and a single-qubit measurement. The measurement outcome indicates whether the two input qubits were the same (\mbox{$\ket{0}\ket{0}$}, \mbox{$\ket{1}\ket{1}$}) or different (\mbox{$\ket{0}\ket{1}$}, \mbox{$\ket{1}\ket{0}$}). See Sec.~\ref{sec:bell_proj} for a simple linear optics construction for this operation.}\label{fig:parity_meas}\index{Bell measurements}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.39\textwidth]{entanglement_purification}
\captionspacefig \caption{Protocol for entanglement purification of two noisy Bell pairs (blue) into a single less noisy Bell pair. Not shown are trivial single-qubit local corrections that may need to be made, depending upon measurement outcomes.} \label{fig:ent_purif_circ}\index{Entanglement purification protocol}
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function ThreeQubitCode($\ket\psi$):
\begin{enumerate}
\item Using two CNOT gates, redundantly encode the logical single-qubit state,
\begin{align}
\ket\psi=\alpha\ket{0}+\beta\ket{1},
\end{align}
into the 3-qubit state,
\begin{align}
\ket\psi_R &= \hat{\mathrm{CNOT}}_{1,2}\hat{\mathrm{CNOT}}_{1,3}\ket\psi\ket{00} \nonumber \\
&= \alpha\ket{000}+\beta\ket{111}.
\end{align}
\item Independently apply bit-flip channels $\mathcal{E}_X$ to each of the three encoded qubits.
\item If exactly one bit-flip operation was applied in total, the three possible erroneous encoded states are,
\begin{align}
\ket\psi_1 &= \hat{X}_1 \ket\psi_R = \alpha\ket{001}+\beta\ket{110}, \nonumber \\
\ket\psi_2 &= \hat{X}_2 \ket\psi_R = \alpha\ket{010}+\beta\ket{101}, \nonumber \\
\ket\psi_3 &= \hat{X}_3 \ket\psi_R = \alpha\ket{100}+\beta\ket{011}.
\end{align}
\item Determine the parity of each of the three pairs of encoded qubits.
\item Assuming at most a single bit-flip operation has occurred on the encoded state, the three parity outcomes uniquely determine which encoded qubit the bit-flip was applied to.
\item Apply classically-controlled bit-flip recovery operations, $\mathcal{R}$, to correct the encoded state, recovering $\ket\psi_R$.
\item Apply the inverse of the encoding operation to recover $\ket\psi$.
\item $\Box$
\end{enumerate}}
\begin{align}
\Qcircuit @C=1.3em @R=.6em {
  & \lstick{\ket{\psi}} & \ctrl{2} & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{3}  & \qw       & \ctrl{4} & \qw & \multigate{2}{\ \mathcal{R}\ } & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{2}  & \ctrl{2}  & \qw      & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \qw       & \ctrl{2}  & \ctrl{3} & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  &          &          &          & & \lstick{\ket{0}} & \targ \qw & \qw       & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \targ \qw & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \qw       & \targ    & \meter & \control \cw \cwx
} \nonumber
\end{align}
\end{mdframed}
\captionspacealg \caption{3-qubit code for protecting against at most a single logical bit-flip error. The doubly-controlled CNOT gates represent parity measurements, \mbox{$n_3=n_1\oplus n_2$}, where $n_i$ represents the value of the $i$th qubit. In a Hadamard-rotated basis, the same circuit may be employed to protect against a single phase-flip error. And by concatenating the two we obtain a 9-qubit code protecting against a single depolarising error (i.e joint bit-flip/phase-flip), which is a universal single-qubit error model.} \label{alg:three_QEC}
\end{table}

@@

\if 2\pubmode
	\begin{figure}[!htbp]
		\includegraphics[width=0.475\textwidth]{torus}\\
		\includegraphics[width=0.475\textwidth]{toric_code}
		\captionspacefig \caption{Graph representation of the toric QEC code, and its associated stabilisers. The graph resides on a torus (top), while the physical qubits reside on the embedded lattice (bottom). The star and plaquette stabilisers across all vertices, jointly specify the state of the graph up to two missing degrees of freedom, which encode a single logical qubit. Thus, a logical qubit is encoded jointly across the entire graph, not at any specific vertex. Logical operations are performed via operations following topological paths through the lattice (not shown). The graph may be distributed across multiple hosts for distributed quantum computation.} \label{fig:toric_code}
	\end{figure}
\else
	\begin{figure*}[!htbp]
		\includegraphics[width=0.475\textwidth]{torus}
		\includegraphics[width=0.475\textwidth]{toric_code}
		\captionspacefig \caption{Graph representation of the toric QEC code, and its associated stabilisers. The graph resides on a torus (left), while the physical qubits reside on the embedded lattice (right). The star and plaquette stabilisers across all vertices, jointly specify the state of the graph up to two missing degrees of freedom, which encode a single logical qubit. Thus, a logical qubit is encoded jointly across the entire graph, not at any specific vertex. Logical operations are performed via operations following topological paths through the lattice (not shown). The graph may be distributed across multiple hosts for distributed quantum computation.} \label{fig:toric_code}
	\end{figure*}
\fi

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.3\textwidth]{toric_code_correction}
	\captionspacefig \caption{QEC of a single bit-flip (top) and phase-flip (bottom) error via measuring two overlapping stabilisers. If there is at most one bit- or phase-flip error, as per this graphic, then upon measuring all the star and plaquette stabilisers, only those whose qubits are affected by the error channel will yield the $-1$ measurement outcome, the others all yielding $+1$. Such an error will affect exactly two stabilisers, whose qubit in common must have been the one affected by the respective error, which can subsequently be corrected since the type of the error and its location are known. Thus, in this example, all of the $\hat{S}_+^{(1)}$, $\hat{S}_+^{(2)}$, $\hat{S}_\square^{(1)}$ and $\hat{S}_\square^{(2)}$ stabilisers will yield $-1$ outcomes for the shown $\hat{X}$ and $\hat{Z}$ errors, whereas any of the remaining (not shown) $\hat{S}_k^{(j)}$ will yield $+1$ outcomes, which uniquely specifies where those errors took place.}\label{fig:toric_corr}	
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{torus_paulis}
	\captionspacefig \caption{Implementation of logical Pauli-$\hat{X}$ (\comment{which colour?}) and -$\hat{Z}$ (\comment{which colour?}) operations on a toric code qubit via the application of a chain of local Paulis. The chains must circumnavigate the torus around either axis. Any path topologically equivalent to such a circumnavigation of the torus is sufficient, enabling paths to bypass defects in the lattice.} \label{fig:toric_code_paulis}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{unitary_error_averaging}
\captionspacefig \caption{Protocol for error correction via unitary error averaging. Here our computation resides across \mbox{$N=2$} modes, and there are \mbox{$M=2$} redundant copies of the manufactured unitary, which straightforwardly generalises to arbitrary $M$ and $N$. A fanout operation splits the wave amplitudes from the set of $N$ input modes uniformly across $M$ sets of $N$ modes. Each set of $N$ evolves through an independent copy of the manufactured imperfect unitary, $\tilde{U}_i$. A reverse fanout operation recollects the bundles of modes. Upon post-selecting upon detecting all photons within the first $N$ modes, and none in the other ancillary modes, the state is projected into the subspace as if it had been acted upon by the arithmetic average of the imperfect unitaries. If photons are detected in the error modes, our logical state has effectively suffered photon loss and has been corrupted.} \label{fig:error_av_circuit}	
\end{figure}

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{bloch_sphere_dyn_dec_long}
	\captionspacefig \caption{Bloch sphere representation of a sequence to dynamically decouple an unknown $\hat{Z}$ rotation from a qubit. (a) Blue dot represents the initial state. (b) The state undergoes an unknown $\hat{Z}(\theta)$ rotation. (c) A bit-flip ($\hat{X}$) flips the Bloch sphere upside down. (d) Waiting for the same time as before such that the same unknown $\hat{Z}$-rotation takes place, the state ends up in its initial state, independent of the $\hat{Z}$-rotation angle $\theta$, but assuming it was the same on both occasions in (b) and (d).} \label{fig:bloch_sphere_dyn_dec}	
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=\textwidth]{bloch_sphere_dyn_dec}
	\captionspacefig \caption{Bloch sphere representation of a sequence to dynamically decouple an unknown $\hat{Z}$ rotation from a qubit. (a) Blue dot represents the initial state. (b) The state undergoes an unknown $\hat{Z}(\theta)$ rotation. (c) A bit-flip ($\hat{X}$) flips the Bloch sphere upside down. (d) Waiting for the same time as before such that the same unknown $\hat{Z}$-rotation takes place, the state ends up in its initial state, independent of the $\hat{Z}$-rotation angle $\theta$, but assuming it was the same on both occasions in (b) and (d).} \label{fig:bloch_sphere_dyn_dec}	
	\end{figure*}
\fi

### 2018-09-03 Sections/routing_strategies.tex

The very trivial algorithm for this route finding is shown in Alg.~\ref{alg:single_user}, where the \texttt{ShortestPath()} function could be any of the existing, well-known shortest path algorithms (Sec.~\ref{sec:shortest_path}).
\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{ 
function Strategy.SingleUser(Packets):
\begin{enumerate}
    \item for(packet$\in$Packets) \{
        \setlength{\itemindent}{.2in}
                \item currentNode = packet.RoutingQueue.Pop()
        \item shortestRoute = \\
        ShortestPath(currentNode,packet.Recipient)
        \item packet.RoutingQueue.Flush()
        \item packet.RoutingQueue.Push(shortestRoute)
    \setlength{\itemindent}{0in}
    \item \}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{For a single user, a simple shortest-path algorithm necessarily finds the optimal route, as there is no potential for packet collisions or competition for network resources.} \label{alg:single_user}
\end{table}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{conflict}
\captionspace \caption{A simple network with two competing pairs of senders and receivers, \mbox{$A_1\to B_1$} and \mbox{$A_2\to B_2$}. Edges are labelled by \mbox{$\{b,d\}$}, where $b$ is the bandwidth attribute of the link (i.e number of states that can be communicated simultaneously), and $d$ is the cost metric associated with the link, e.g loss in dB. (blue line) $R_1$ and $R_2$ are two routes from $A_2\to B_2$. Either of these routes could be declared optimal, depending on the choice of cost function. For a trivial additive cost function, $R_2$ would be declared optimal. (red lines) $R_3$ is the optimal route from \mbox{$A_1\to B_1$}.} \label{fig:conflict}
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Strategy.RoundRobin(Packets):
\begin{enumerate}
    \item for(packet$\in$Packets) \{
        \setlength{\itemindent}{.2in}
                \item currentNode = packet.RoutingQueue.Pop()
        \item shortestRoute = \\
        ShortestPath(currentNode,packet.Recipient)
        \item packet.RoutingQueue.Flush()
        \item packet.RoutingQueue.Push(shortestRoute)
    \setlength{\itemindent}{0in} \}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{In the \textsc{Round Robin} strategy we simply iterate through the list of active packets, with no regard for any metrics, or conflicts between them. Rather, we strive for perfect time-sharing equality, and every packet entirely ignores the actions of all other packets, performing a completely selfish optimisation strategy.} \label{alg:round_robin}
\end{table}
The \textsc{Round Robin} strategy can be considered base skeleton code for more sophistic algorithms to build upon, simply by reordering the packet queue.

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Strategy.CostPriority(Packets):
\begin{enumerate}
    \item packetsAndCosts = []
    \item for(packet$\in$Packets) \{
        \setlength{\itemindent}{.2in}
        \item cost = costFunction(packet)
        \item packetsAndCosts.Append([packet,cost])
    \setlength{\itemindent}{0in}
    \item     \}
    \item sorted = \\
        SortByCostDescending(packetsAndCosts)
    \item for(packet$\in$sorted) \{
        \setlength{\itemindent}{.2in}
        \item currentNode = packet.RoutingQueue.Pop()
        \item shortestRoute = \\
        ShortestPath(currentNode,packet.Recipient)
        \item packet.RoutingQueue.Flush()
        \item packet.RoutingQueue.Push(shortestRoute)
    \setlength{\itemindent}{0in}
    \item \}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{The \textsc{Cost Priority} strategy scheduling algorithm that gives highest routing priority to \textsc{Packets} with the highest accumulated cost (i.e which have suffered the most). The as-yet undefined \texttt{costFunction()}, which refers to $f_\mathrm{cost}$ from Eq.~(\ref{eq:net_cost_R}), is where the details of the priority decisions are made, which could be entirely arbitrary. In this example, the shortest route is recalculated at each step, based on the expectation that network metrics are dynamic.} \label{alg:cost_prior_alg}
\end{table}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Strategy.AllOrNothing(Packets, threshold):
\begin{enumerate}
    \item for(packet$\in$Packets) \{
        \setlength{\itemindent}{.2in}
        \item cost = packet.costFunction()
        \item if(cost $\geq$ threshold) \{
        \setlength{\itemindent}{.4in}
            \item packet.Sender.Notify(\textsc{Failure})
            \item packet.Recipient.Notify(\textsc{Failure})
            \item packet.Discard()
                    \setlength{\itemindent}{.2in}
            \item \}
        \setlength{\itemindent}{0in}
    \item \}
    \item Strategy.SomeOtherStrategy(Packets)
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{The \textsc{All or Nothing} strategy. If the net cost of a packet exceeds a certain \texttt{threshold}, it is discarded outright, and the sender and recipient notified.} \label{alg:all_or_nothing}
\end{table}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Strategy.OptimalFlow(Packets):
\begin{enumerate}
    \item routes = Packets.OptimalFlowRoutes()
    \item for(packet$\in$Packets) \{
        \setlength{\itemindent}{.2in}
                \item packet.RoutingQueue.Flush()
                \item packet.RoutingQueue.Push(routes[packet])
                \setlength{\itemindent}{0in} 
    \item \}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{A generic optimal flow routing strategy. \textsc{Packets} is the array of all packets that ought to be transmitted simultaneously, which are collectively optimised using some flow optimisation algorithm before undergoing transport.} \label{alg:opt_flow}
\end{table}

>>>>

The very trivial algorithm for this route finding is shown in Alg.~\ref{alg:single_user}, where the \texttt{ShortestPath()} function could be any of the existing, well-known shortest path algorithms (Sec.~\ref{sec:shortest_path}).
\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{ 
function Strategy.SingleUser(Packets):
\begin{enumerate}
    \item for(packet$\in$Packets) \{
        \setlength{\itemindent}{.2in}
                \item currentNode = packet.RoutingQueue.Pop()
        \item shortestRoute = \\
        ShortestPath(currentNode,packet.Recipient)
        \item packet.RoutingQueue.Flush()
        \item packet.RoutingQueue.Push(shortestRoute)
    \setlength{\itemindent}{0in}
    \item \}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{For a single user, a simple shortest-path algorithm necessarily finds the optimal route, as there is no potential for packet collisions or competition for network resources.} \label{alg:single_user}
\end{table}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{conflict}
\captionspacefig \caption{A simple network with two competing pairs of senders and receivers, \mbox{$A_1\to B_1$} and \mbox{$A_2\to B_2$}. Edges are labelled by \mbox{$\{b,d\}$}, where $b$ is the bandwidth attribute of the link (i.e number of states that can be communicated simultaneously), and $d$ is the cost metric associated with the link, e.g loss in dB. (blue line) $R_1$ and $R_2$ are two routes from $A_2\to B_2$. Either of these routes could be declared optimal, depending on the choice of cost function. For a trivial additive cost function, $R_2$ would be declared optimal. (red lines) $R_3$ is the optimal route from \mbox{$A_1\to B_1$}.} \label{fig:conflict}
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Strategy.RoundRobin(Packets):
\begin{enumerate}
    \item for(packet$\in$Packets) \{
        \setlength{\itemindent}{.2in}
                \item currentNode = packet.RoutingQueue.Pop()
        \item shortestRoute = \\
        ShortestPath(currentNode,packet.Recipient)
        \item packet.RoutingQueue.Flush()
        \item packet.RoutingQueue.Push(shortestRoute)
    \setlength{\itemindent}{0in} \}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{In the \textsc{Round Robin} strategy we simply iterate through the list of active packets, with no regard for any metrics, or conflicts between them. Rather, we strive for perfect time-sharing equality, and every packet entirely ignores the actions of all other packets, performing a completely selfish optimisation strategy.} \label{alg:round_robin}
\end{table}
The \textsc{Round Robin} strategy can be considered base skeleton code for more sophistic algorithms to build upon, simply by reordering the packet queue.

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Strategy.CostPriority(Packets):
\begin{enumerate}
    \item packetsAndCosts = []
    \item for(packet$\in$Packets) \{
        \setlength{\itemindent}{.2in}
        \item cost = costFunction(packet)
        \item packetsAndCosts.Append([packet,cost])
    \setlength{\itemindent}{0in}
    \item     \}
    \item sorted = \\
        SortByCostDescending(packetsAndCosts)
    \item for(packet$\in$sorted) \{
        \setlength{\itemindent}{.2in}
        \item currentNode = packet.RoutingQueue.Pop()
        \item shortestRoute = \\
        ShortestPath(currentNode,packet.Recipient)
        \item packet.RoutingQueue.Flush()
        \item packet.RoutingQueue.Push(shortestRoute)
    \setlength{\itemindent}{0in}
    \item \}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{The \textsc{Cost Priority} strategy scheduling algorithm that gives highest routing priority to \textsc{Packets} with the highest accumulated cost (i.e which have suffered the most). The as-yet undefined \texttt{costFunction()}, which refers to $f_\mathrm{cost}$ from Eq.~(\ref{eq:net_cost_R}), is where the details of the priority decisions are made, which could be entirely arbitrary. In this example, the shortest route is recalculated at each step, based on the expectation that network metrics are dynamic.} \label{alg:cost_prior_alg}
\end{table}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Strategy.AllOrNothing(Packets, threshold):
\begin{enumerate}
    \item for(packet$\in$Packets) \{
        \setlength{\itemindent}{.2in}
        \item cost = packet.costFunction()
        \item if(cost $\geq$ threshold) \{
        \setlength{\itemindent}{.4in}
            \item packet.Sender.Notify(\textsc{Failure})
            \item packet.Recipient.Notify(\textsc{Failure})
            \item packet.Discard()
                    \setlength{\itemindent}{.2in}
            \item \}
        \setlength{\itemindent}{0in}
    \item \}
    \item Strategy.SomeOtherStrategy(Packets)
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{The \textsc{All or Nothing} strategy. If the net cost of a packet exceeds a certain \texttt{threshold}, it is discarded outright, and the sender and recipient notified.} \label{alg:all_or_nothing}
\end{table}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Strategy.OptimalFlow(Packets):
\begin{enumerate}
    \item routes = Packets.OptimalFlowRoutes()
    \item for(packet$\in$Packets) \{
        \setlength{\itemindent}{.2in}
                \item packet.RoutingQueue.Flush()
                \item packet.RoutingQueue.Push(routes[packet])
                \setlength{\itemindent}{0in} 
    \item \}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{A generic optimal flow routing strategy. \textsc{Packets} is the array of all packets that ought to be transmitted simultaneously, which are collectively optimised using some flow optimisation algorithm before undergoing transport.} \label{alg:opt_flow}
\end{table}

### 2018-09-03 Sections/the_irrelevance_of_latency.tex

Teleportation-based quantum communication is additionally favourable in that shared Bell pairs can be purified before being utilised, allowing errors accrued during quantum communication to be minimised, something not so straightforward when transmitting data qubits directly.

>>>>

Teleportation-based quantum communication is additionally favourable in that shared Bell pairs can be purified before being utilised, allowing errors accrued during quantum communication to be minimised, something not so straightforward (or impossible) when transmitting data qubits directly.
